
% Default to the notebook output style


% Inherit from the specified cell style.





    
\documentclass{article}

    
    

    \usepackage{graphicx} % Used to insert images
    \usepackage{adjustbox} % Used to constrain images to a maximum size 
    \usepackage{color} % Allow colors to be defined
    \usepackage{enumerate} % Needed for markdown enumerations to work
    \usepackage{geometry} % Used to adjust the document margins
    \usepackage{amsmath} % Equations
    \usepackage{amssymb} % Equations
    \usepackage{eurosym} % defines \euro
    \usepackage[mathletters]{ucs} % Extended unicode (utf-8) support
    \usepackage[utf8x]{inputenc} % Allow utf-8 characters in the tex document
    \usepackage{fancyvrb} % verbatim replacement that allows latex
    \usepackage{grffile} % extends the file name processing of package graphics 
                         % to support a larger range 
    % The hyperref package gives us a pdf with properly built
    % internal navigation ('pdf bookmarks' for the table of contents,
    % internal cross-reference links, web links for URLs, etc.)
    \usepackage{hyperref}
    \usepackage{longtable} % longtable support required by pandoc >1.10
    \usepackage{booktabs}  % table support for pandoc > 1.12.2
    
\usepackage{color}
\usepackage{soul}
\usepackage[framemethod=tikz]{mdframed}


    
    
    \definecolor{orange}{cmyk}{0,0.4,0.8,0.2}
    \definecolor{darkorange}{rgb}{.71,0.21,0.01}
    \definecolor{darkgreen}{rgb}{.12,.54,.11}
    \definecolor{myteal}{rgb}{.26, .44, .56}
    \definecolor{gray}{gray}{0.45}
    \definecolor{lightgray}{gray}{.95}
    \definecolor{mediumgray}{gray}{.8}
    \definecolor{inputbackground}{rgb}{.95, .95, .85}
    \definecolor{outputbackground}{rgb}{.95, .95, .95}
    \definecolor{traceback}{rgb}{1, .95, .95}
    % ansi colors
    \definecolor{red}{rgb}{.6,0,0}
    \definecolor{green}{rgb}{0,.65,0}
    \definecolor{brown}{rgb}{0.6,0.6,0}
    \definecolor{blue}{rgb}{0,.145,.698}
    \definecolor{purple}{rgb}{.698,.145,.698}
    \definecolor{cyan}{rgb}{0,.698,.698}
    \definecolor{lightgray}{gray}{0.5}
    
    % bright ansi colors
    \definecolor{darkgray}{gray}{0.25}
    \definecolor{lightred}{rgb}{1.0,0.39,0.28}
    \definecolor{lightgreen}{rgb}{0.48,0.99,0.0}
    \definecolor{lightblue}{rgb}{0.53,0.81,0.92}
    \definecolor{lightpurple}{rgb}{0.87,0.63,0.87}
    \definecolor{lightcyan}{rgb}{0.5,1.0,0.83}
    
    % commands and environments needed by pandoc snippets
    % extracted from the output of `pandoc -s`
    \providecommand{\tightlist}{%
      \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
    \DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
    % Add ',fontsize=\small' for more characters per line
    \newenvironment{Shaded}{}{}
    \newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{{#1}}}}
    \newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.56,0.13,0.00}{{#1}}}
    \newcommand{\DecValTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
    \newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
    \newcommand{\FloatTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
    \newcommand{\CharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
    \newcommand{\StringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
    \newcommand{\CommentTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textit{{#1}}}}
    \newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{{#1}}}
    \newcommand{\AlertTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{{#1}}}}
    \newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.02,0.16,0.49}{{#1}}}
    \newcommand{\RegionMarkerTok}[1]{{#1}}
    \newcommand{\ErrorTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{{#1}}}}
    \newcommand{\NormalTok}[1]{{#1}}
    
    % Define a nice break command that doesn't care if a line doesn't already
    % exist.
    \def\br{\hspace*{\fill} \\* }
    % Math Jax compatability definitions
    \def\gt{>}
    \def\lt{<}
    % Document parameters
    \title{export\_highlights}
    
    
\author{}

    

    % Pygments definitions
    
\makeatletter
\def\PY@reset{\let\PY@it=\relax \let\PY@bf=\relax%
    \let\PY@ul=\relax \let\PY@tc=\relax%
    \let\PY@bc=\relax \let\PY@ff=\relax}
\def\PY@tok#1{\csname PY@tok@#1\endcsname}
\def\PY@toks#1+{\ifx\relax#1\empty\else%
    \PY@tok{#1}\expandafter\PY@toks\fi}
\def\PY@do#1{\PY@bc{\PY@tc{\PY@ul{%
    \PY@it{\PY@bf{\PY@ff{#1}}}}}}}
\def\PY#1#2{\PY@reset\PY@toks#1+\relax+\PY@do{#2}}

\expandafter\def\csname PY@tok@gp\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,0.50}{##1}}}
\expandafter\def\csname PY@tok@no\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.53,0.00,0.00}{##1}}}
\expandafter\def\csname PY@tok@il\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@sx\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@kt\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.69,0.00,0.25}{##1}}}
\expandafter\def\csname PY@tok@mo\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@sh\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@bp\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@gd\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.63,0.00,0.00}{##1}}}
\expandafter\def\csname PY@tok@sb\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@err\endcsname{\def\PY@bc##1{\setlength{\fboxsep}{0pt}\fcolorbox[rgb]{1.00,0.00,0.00}{1,1,1}{\strut ##1}}}
\expandafter\def\csname PY@tok@nd\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.67,0.13,1.00}{##1}}}
\expandafter\def\csname PY@tok@gr\endcsname{\def\PY@tc##1{\textcolor[rgb]{1.00,0.00,0.00}{##1}}}
\expandafter\def\csname PY@tok@kd\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@s\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@cs\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@sd\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@ss\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@nn\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@w\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.73,0.73}{##1}}}
\expandafter\def\csname PY@tok@kn\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@sc\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@s1\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@ge\endcsname{\let\PY@it=\textit}
\expandafter\def\csname PY@tok@cp\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.74,0.48,0.00}{##1}}}
\expandafter\def\csname PY@tok@gh\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,0.50}{##1}}}
\expandafter\def\csname PY@tok@gi\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.63,0.00}{##1}}}
\expandafter\def\csname PY@tok@vc\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@si\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.73,0.40,0.53}{##1}}}
\expandafter\def\csname PY@tok@ow\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.67,0.13,1.00}{##1}}}
\expandafter\def\csname PY@tok@vg\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@sr\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.40,0.53}{##1}}}
\expandafter\def\csname PY@tok@cm\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@c\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@mi\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@kc\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@ne\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.82,0.25,0.23}{##1}}}
\expandafter\def\csname PY@tok@nf\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@go\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.53,0.53,0.53}{##1}}}
\expandafter\def\csname PY@tok@m\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@mh\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@nc\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@mb\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@se\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.73,0.40,0.13}{##1}}}
\expandafter\def\csname PY@tok@gt\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.27,0.87}{##1}}}
\expandafter\def\csname PY@tok@nv\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@c1\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@kp\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@s2\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@nb\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@ni\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.60,0.60,0.60}{##1}}}
\expandafter\def\csname PY@tok@k\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@na\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.49,0.56,0.16}{##1}}}
\expandafter\def\csname PY@tok@o\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@mf\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@nl\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.63,0.63,0.00}{##1}}}
\expandafter\def\csname PY@tok@nt\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@gs\endcsname{\let\PY@bf=\textbf}
\expandafter\def\csname PY@tok@vi\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@gu\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.50,0.00,0.50}{##1}}}
\expandafter\def\csname PY@tok@kr\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}

\def\PYZbs{\char`\\}
\def\PYZus{\char`\_}
\def\PYZob{\char`\{}
\def\PYZcb{\char`\}}
\def\PYZca{\char`\^}
\def\PYZam{\char`\&}
\def\PYZlt{\char`\<}
\def\PYZgt{\char`\>}
\def\PYZsh{\char`\#}
\def\PYZpc{\char`\%}
\def\PYZdl{\char`\$}
\def\PYZhy{\char`\-}
\def\PYZsq{\char`\'}
\def\PYZdq{\char`\"}
\def\PYZti{\char`\~}
% for compatibility with earlier versions
\def\PYZat{@}
\def\PYZlb{[}
\def\PYZrb{]}
\makeatother



    

    
    % Prevent overflowing lines due to hard-to-break entities
    \sloppy 
    % Setup hyperref package
    \hypersetup{
      breaklinks=true,  % so long urls are correctly broken across lines
      colorlinks=true,
      urlcolor=blue,
      linkcolor=darkorange,
      citecolor=darkgreen,
      }
    % Slightly bigger margins than the latex defaults
    
    \geometry{verbose,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}
    
    
    \newcommand{\highlighta}[1]{{\sethlcolor{yellow} \textcolor{red}{\hl{#1}}}}
    \newcommand{\highlightb}[1]{{\sethlcolor{red} \textcolor{yellow}{\hl{#1}}}}
    \newcommand{\highlightc}[1]{{\sethlcolor{green} \textcolor{yellow}{\hl{#1}}}}
    \newenvironment{highlightA}{\begin{mdframed}[hidealllines=true,backgroundcolor=yellow!20]}{\end{mdframed}}
    \newenvironment{highlightB}{\begin{mdframed}[hidealllines=true,backgroundcolor=red!20]}{\end{mdframed}}
    \newenvironment{highlightC}{\begin{mdframed}[hidealllines=true,backgroundcolor=green!20]}{\end{mdframed}}


%\usepackage{foo}

    \begin{document}
    
    
    \maketitle
    
    

    
    \section{Exporting the notebook}\label{exporting-the-notebook}

As suggested by @juhasch, it is interesting to keep the highlights when
exporting the notebook to another format. We give and explain below some
possibilities:

    \subsection{Short version}\label{short-version}

\begin{itemize}
\item
  Html export:

\begin{Shaded}
\begin{Highlighting}[]
 \KeywordTok{jupyter} \NormalTok{nbconvert FILE  --config JUPYTER_DATA_DIR/extensions/highlight_html_cfg.py }
\end{Highlighting}
\end{Shaded}
\item
  LaTeX export:

\begin{Shaded}
\begin{Highlighting}[]
 \KeywordTok{jupyter} \NormalTok{nbconvert FILE  --config JUPYTER_DATA_DIR/extensions/highlight_latex_cfg.py }
\end{Highlighting}
\end{Shaded}

  where JUPYTER\_DATA\_DIR can be found from the output of

\begin{Shaded}
\begin{Highlighting}[]
 \KeywordTok{jupyter} \NormalTok{--paths}
\end{Highlighting}
\end{Shaded}

  eg \texttt{\textasciitilde{}/.local/share/jupyter} in my case. Seems
  to be
  \texttt{c:\textbackslash{}users\textbackslash{}NAME\textbackslash{}AppData\textbackslash{}Roaming\textbackslash{}jupyter}
  under Windows.
\end{itemize}

Examples can be found here: \href{tst_highlights.ipynb}{initial
notebook}, \href{tst_highlights.html}{html version},
\href{tst_highlights.pdf}{pdf version} (after an additional LaTeX
\(\rightarrow\) pdf compilation).

    \subsection{Html export}\label{html-export}

This is quite easy. Actually, highlight formatting embedded in markdown
cells is preserved while converting with the standard

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{jupyter} \NormalTok{nbconvert file.ipynb}
\end{Highlighting}
\end{Shaded}

However, the css file is missing and must be added. Here we have several
possibilities

\begin{itemize}
\item
  Embed the css \emph{within} the notebook. For that, consider the last
  cell of the present notebook. This code reads the css file
  \texttt{highlighter.css} in the extension directory and displays the
  corresponding style. So doing the
  \texttt{\textless{}style\textgreater{}\ ...\textless{}/style\textgreater{}}
  section will be present in the cell output and interpreted by the web
  browser. Drawbacks of this solution is that user still have to execute
  this cell and that the this is not language agnostic.
\item
  Use a \textbf{template file} to link or include the css file during
  conversion. Such a file is provided as
  \texttt{templates/highlighter.tpl}. It was choosen here to
  \emph{include} the css content in the produced html file rather than
  linking it. This avoids the necessity to keep the css file with the
  html files.
\item
  This works directly if the css resides in the same directory as the
  file the user is attempting to convert --thus requires the user to
  copy \texttt{highlighter.css} in the current directory. Then the
  conversion is simply

\begin{Shaded}
\begin{Highlighting}[]
  \KeywordTok{jupyter} \NormalTok{nbconvert file.ipynb --template highlighter}
\end{Highlighting}
\end{Shaded}
\item
  It still remains two problems with this approach. First, it can be
  annoying to have to systematically copy the css file in the current
  directory. Second, the data within the html tags is not converted (and
  thus markdown remains unmodified). A solution is to use a pair of
  preprocessor/postprocessor that modify the html tags and enable the
  subsequent markdown to html converter to operate on the included data.
  Also, a config file is provided which redefines the template path to
  enable direct inclusion of the css file in the extension directory.
  Unfortunately, \highlighta{it seems that the \emph{full path} to
  the config file has to be provided}. This file resides in the
  extensions subdirectory of the jupyter\_data\_dir. The path can be
  found by looking at the output of

\begin{Shaded}
\begin{Highlighting}[]
 \KeywordTok{jupyter} \NormalTok{--paths}
\end{Highlighting}
\end{Shaded}

  Then the command to issue for converting the notebook to html is

\begin{Shaded}
\begin{Highlighting}[]
 \KeywordTok{jupyter} \NormalTok{nbconvert FILE  --config JUPYTER_DATA_DIR/extensions/highlight_html_cfg.py }
\end{Highlighting}
\end{Shaded}
\end{itemize}

For instance

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{jupyter} \NormalTok{nbconvert tst_highlights.ipynb  --config ~/.local/share/jupyter/extensions/highlight_html_cfg.py }
\end{Highlighting}
\end{Shaded}

    \subsection{LaTeX export}\label{latex-export}

This is a bit more complicated since the direct conversion removes all
html formatting present in markdown cells. Thus use again a
\textbf{preprocessor} which runs before the markdown \(\rightarrow\)
LaTeX conversion. In turn, it appears that we also need to postprocess
the result.

Three LaTeX commands, namely \emph{highlighta, highlightb, highlightc},
and three environments \emph{highlightA, highlightB, highlightC} are
defined. Highlighting html markup is then transformed into the
corresponding LaTeX commands and the text for completely highlighted
cells is put in the adequate LaTeX environment.

Pre and PostProcessor classes are defined in the file
\texttt{pp\_highlighter.py} located in the \texttt{extensions}
directory. A LaTeX template, that includes the necessary packages and
the definitions of commands/environments is provides as
\texttt{highlighter.tplx} in the template directory. The template
inherits from \texttt{article.ltx}. For more complex scenarios,
typically if the latex template file has be customized, the user shall
modify its template or inherit from his base template rather than from
article.

Finally, a config file fixes the different options for the conversion.
Then the command to issue is simply

\begin{Shaded}
\begin{Highlighting}[]
 \KeywordTok{jupyter} \NormalTok{nbconvert FILE  --config JUPYTER_DATA_DIR/extensions/highlight_latex_cfg.py }
\end{Highlighting}
\end{Shaded}

e.g.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{jupyter} \NormalTok{nbconvert tst_highlights.ipynb  --config ~/.local/share/jupyter/extensions/highlight_latex_cfg.py }
\end{Highlighting}
\end{Shaded}

    \subsection{Configuring paths}\label{configuring-paths}

\highlighta{For those who do not have taken the extension from the
\texttt{jupyter_contrib_nbextensions} repository or have not configured
extensions via its \texttt{setup.py} utility,} a file
\texttt{set\_paths.py} is present in the extension directory (it is
merely a verbatim copy of the relevant parts in setup.py). This file
configure the paths to the \texttt{templates} and \texttt{extension}
directories. It should be executed by something like

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{python3} \NormalTok{set_paths.py}
\end{Highlighting}
\end{Shaded}

Additionaly, you may also have to execute \texttt{mv\_paths.py} if you
installed from the original repo via
\texttt{jupyter\ nbextension\ install\ ..}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{python3} \NormalTok{mv_paths.py}
\end{Highlighting}
\end{Shaded}

    \subsection{Example for embedding the css within the notebook before
conversion}\label{example-for-embedding-the-css-within-the-notebook-before-conversion}

    \begin{Verbatim}[commandchars=\\\{\}]
>>> \PY{k+kn}{from} \PY{n+nn}{IPython}\PY{n+nn}{.}\PY{n+nn}{core}\PY{n+nn}{.}\PY{n+nn}{display} \PY{k}{import} \PY{n}{display}\PY{p}{,} \PY{n}{HTML}
... \PY{k+kn}{from} \PY{n+nn}{jupyter\PYZus{}core}\PY{n+nn}{.}\PY{n+nn}{paths} \PY{k}{import} \PY{n}{jupyter\PYZus{}config\PYZus{}dir}\PY{p}{,} \PY{n}{jupyter\PYZus{}data\PYZus{}dir}
... \PY{k+kn}{import} \PY{n+nn}{os}
... \PY{n}{csspath}\PY{o}{=}\PY{n}{os}\PY{o}{.}\PY{n}{path}\PY{o}{.}\PY{n}{join}\PY{p}{(}\PY{n}{jupyter\PYZus{}data\PYZus{}dir}\PY{p}{(}\PY{p}{)}\PY{p}{,}\PY{l+s}{\PYZsq{}}\PY{l+s}{nbextensions}\PY{l+s}{\PYZsq{}}\PY{p}{,}
...                        \PY{l+s}{\PYZsq{}}\PY{l+s}{highlighter}\PY{l+s}{\PYZsq{}}\PY{p}{,}\PY{l+s}{\PYZsq{}}\PY{l+s}{highlighter.css}\PY{l+s}{\PYZsq{}}\PY{p}{)}
... \PY{n}{HTML}\PY{p}{(}\PY{l+s}{\PYZsq{}}\PY{l+s}{\PYZlt{}style\PYZgt{}}\PY{l+s}{\PYZsq{}}\PY{o}{+}\PY{n+nb}{open}\PY{p}{(}\PY{n}{csspath}\PY{p}{,} \PY{l+s}{\PYZdq{}}\PY{l+s}{r}\PY{l+s}{\PYZdq{}}\PY{p}{)}\PY{o}{.}\PY{n}{read}\PY{p}{(}\PY{p}{)}\PY{o}{+}\PY{l+s}{\PYZsq{}}\PY{l+s}{\PYZlt{}/style\PYZgt{}}\PY{l+s}{\PYZsq{}}\PY{p}{)}
    \end{Verbatim}

    
    
    \begin{verbatim}
<IPython.core.display.HTML object>
    \end{verbatim}

    


    % Add a bibliography block to the postdoc
    
    
    
    \end{document}
